Supplementary Materials: School Socioeconomic Status Context and Social Skills in Children

### 2020-11-06 manuscript.Rmd
Ed Researcher Version

- name: Philip Parker
  affiliation: '1'
  corresponding: yes
  address: 33 Berry St, North Sydney, NSW, 2060, Australia
  email: philip.parker@acu.edu.au
  role:
  - Conceptualization
  - Formal Analysis
  - Data curation
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Taren Sanders
  affiliation: '1'
  # corresponding: no
  # address: 33 Berry St, North Sydney, NSW, 2060, Australia
  # email: taren.sanders@acu.edu.au
  role:
  - Conceptualization
  - Data curation
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Jake Anders
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Nikki Shure
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: John Jerrim
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Michael Noetel
  affiliation: '1,3'
  role:
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Joseph Ciarrochi
  affiliation: '1'
  role:
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
shorttitle: School SES and Social Skills
output:
  pdf: papaja::apa6_pdf
  html_document:
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
  word: papaja::apa6_doc
  html_notebook:
    fig_caption: yes
    toc: yes
    highlight: haddock
    theme: spacelab
authornote: |
  Code for this paper is avaliable from [OSF](https://osf.io/q26ej/?view_only=73f60cea7a9c4e6f8affc412b30df118). Data is avaliable from the [Australian Data Archive](https://dataverse.ada.edu.au/dataverse/ada?q=LSAC).
abstract: |2
  As researchers and policymakers try to understand the consequences of SES for educational and occupational attainment, they increasingly consider social skills to be critical. Yet little research has considered how the school socio-economic context may differentially promote or hinder social skill development. In a representative longitudinal sample of  `r nrow(data)` Australian 8-year olds, we tested the association between school average socioeconomic status and social skills as reported by parents and teachers. All models controlled for prior social skills at age 4, and additional school and student covariates. We found that school context was associated with social skill assimilation: controlling for individual socioeconomic status, children in more advantaged schools had more prosocial behavior and fewer peer and conduct problems. We found a consistent interaction between individual and school average socioeconomic status that suggested assimilation effects were only present for children from low socioeconomic backgrounds. We found that children from low socioeconomic backgrounds enter school with lower average social skills. They are more likely to be enrolled in more disadvantaged schools. Finally, the social skills of children from low socioeconomic backgrounds worsen in low SES contexts. Taking the evidence together, social stratified schools may harm children from low SES backgrounds while not benefiting children from high SES backgrounds.
keywords: social skills; assimilation effects; socioeconomic status; school context
wordcount: 4627
bibliography: r-references.bib
floatsintext: no
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Institute for Positive Psychology and Education, Australian Catholic
    University
- id: '2'
  institution: UCL Institute of Education, UCL
- id: '3'
  institution: School of Health and Behavioural Sciences, Australian Catholic University
---

@@

```{r consort,fig.height=4,fig.width=2, fig.cap = 'Participant flow diagramme'}
knitr::include_graphics(here::here('fig','flow.pdf'))
```

We use data for children, their parents, and their teachers from the B-Cohort and K-Cohort of the Longitudinal Study of Australian Children (LSAC). LSAC is a government-run study of a representative sample of Australian children who were zero-one (B-cohort) or four-five (K-Cohort) years of age in 2004. Both cohorts of children have been followed every two years since [@aifs2015]. LSAC includes linked administration records for student performance in a standardized national numeracy test. We also use government collected data on school average socioeconomic status. Many children in the sample were the only child surveyed (`r school_one`) or were one of two children surveyed (`r school_two`) in their school. By using administrative records, we gain school average socioeconomic status based on the child's $\text{\underline{whole}}$ school grade from a high-quality source, thus avoiding sampling bias present in much school context research. We excluded participants who were not in school (e.g., were home schooled, or were otherwise missing an identifier of which school they attended), were not in Year 3 at the time of testing, or were not eligible to complete national standardized testing (e.g., children with an intellectual disability). Together our total sample was `r nrow(data)` (`r boys` boys) children in Year 3 at school (\~age 8). In the vast majority of cases (98% <!--# @philip.parker@acu.edu.au should extract this from data rather than previous research? -->), parent data came from mothers. A participant flow diagram is presented in Figure \@ref(fig:consort) including the number of participants excluded because there were a) not in Year 3 during the age 8 LSAC data collection sweep; b) were not eligible to participate NAPLAN (e.g., due to intellectual disability; or c) were not enrolled in school (e.g., were home schooled).

@@

Social skills were estimated using the peer problems, conduct problems, and prosocial behavior component scores from the SDQ [@goodman1997]. We explored social skills at age 4-5 (for prior social skills; parent report only) and age 8-9 (as primary outcomes) as reported by the child's *parent* and the child's *teacher*. The SDQ asks respondents to rate a child's behavior in the last six months on a 3-point scale (not true, somewhat true, and certainly true). Questions ask about the child's peer problems ("Rather solitary, tends to play alone"), conduct problems ("Often fights with other children or bullies them"), and prosociality ("Is kind to younger children"). Greatest lower bound estimates of reliability were all greater than .95 and parallel analysis suggested that a single component was sufficient for each of the parent and teacher and age 4 and age 8 social skills factors. On the basis of this evidence, we used the total scores for these scales as developed by the LSAC administrators. Scores ranged from 0 to 10. These scores were heavily left censored for peer and conduct problems with a preponderance of students being scored as a zero by their parent or teacher. Prosocial behaviors were heavily right censored. Censoring can be viewed as a special type of missing data where scores on $y*$ (the hypothesised true latent distribution of the variable) below or above the bounds are curtailed to fit within the bounds resulting in the observed scores $y$ [@gelman2020regression]. Models accounting for this censoring were used in all cases with results provided on the scale of the latent variable $y*$ believed to underlie the censored variable (hence negative predicted scores or scores over 10 were possible).

@@

There was a relatively small amount of missing data for most variables. However, given the data were longitudinal and included both linked administrative records and data collected from both the child's teacher and parent, missing data was inevitable. Attrition was offset by applying combined sample and attrition weights constructed for the age 8 sample. Remaining missing data was small with the largest missing data proportion for teacher reported social skills at 14%. All other variables had 6% missing data or less (see code book in [supplementary materials](http://blindedforreview.com/2020_social_skills/supplementary_materials.html)). To account for this, we constructed five imputed datasets using a bootstrapped expectation maximization procedure from the Amelia II package [@honaker2011]. These imputations were used in all analyses. All analyses were done using Bayes via the BRMS package in R [@bürkner2017]. The Bayes models were run once for each imputation and then the resulting posterior samples were pooled before estimates and their uncertainty were extracted. Interactions and their associated uncertainties were plotted by taking marginal effect estimates from a random 500 posterior draws for disadvantaged (two standard deviations below the mean of SES), average, and advantaged (two standard deviations above the mean of SES) students [@gelman2020regression].

@@

Here $X$ is a matrix of individual level predictors for student $i$ including individual SES, prior social skills, gender, cohort, geographic location, and an NAPLAN achievement index. Prior social skills is particularly critical as this provide stronger conclusions that school context rather than selection effects account for the influence of school average SES on student social skills. Put simply the estimate of school average achievement can be interpreted as the influence of school context on the change in children's social skills from age 4 to age 8. $U$ is a matrix of school level predictors for school $j$ including school section and the aforementioned critical variable *school SES*. Note that we predict $y^{*}_{i}$ which is the latent continuous variable underlying the observed variables which are defined as:

@@

In order to provide a context for the main analyses we first aimed to show: a) that children from advantaged backgrounds enter school with better social skills (as measured by their parents) and b) that children in Australia tend to be schooled in socially stratified schools. Student SES is slightly correlated with prosocial behaviour (`r glue::glue("{format(des_social$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_social$prior_ses$fixed[3], digits = 2)}, {format(des_social$prior_ses$fixed[4], digits = 2)}]")`) but more strongly and negatively correlated with conduct (`r glue::glue("{format(des_conduct$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_conduct$prior_ses$fixed[3], digits = 2)}, {format(des_conduct$prior_ses$fixed[4], digits = 2)}]")`) and peer (`r glue::glue("{format(des_peer$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_peer$prior_ses$fixed[3], digits = 2)}, {format(des_peer$prior_ses$fixed[4], digits = 2)}]")`) problems. Children from lower SES backgrounds also tended to enter schools with children from similar backgrounds (`r glue::glue("{format(des_social$sch_ses$fixed[1], digits = 2)} 95% CI[{format(des_social$sch_ses$fixed[3], digits = 2)}, {format(des_social$sch_ses$fixed[4], digits = 2)}]")`).

@@

linear_table %>%
  set_names(str_to_sentence(names(.))) %>%
  printnum() %>%
  apa_table(
  .,
  , caption = "(ref:table-linear)"
  , note = "Results are in unit changes on a 1-10 (Censored) scale for social skills for a standard deviation increase in school SES. Full results in supplementary materials. Conduct = conduct problems, peer = peer problems, social = prosocial. Teacher = teacher reported, parent = parent reported."
)

@@

We next predicted social skills with school average SES controlling for individual SES, a range of demographic covariates and academic performance measures, and social skills at age 4. Results for school average SES are presented under in Table \@ref(table-linear) (the full model results are in [supplementary materials](http://blindedforreview.com/2020_social_skills/supplementary_materials.html)). Because we control for prior social skills, the effects of school average SES in these models can be interpreted as predicting change or development in social skills from age 4 (at or just prior to school enrollment) to age 8 (Year 3). School average SES negatively predicted conduct problems and positively predicted prosocial behavior for both parent and teacher reported social skills. School average SES also negatively predicted peer problems. Results from either teacher or parent provided fairly consistent evidence of the influence of school SES context on social skills (or more specifically change in social skills from age 4 to age 8). Interestingly, the association of school average SES with social skills was similar in strength to the association of individual SES with social skills (see supplementary materials for full results). The effect sizes were equivalent to approximately a 10th of the median absolute deviation in social skills.

@@

interaction_table %>%
  set_names(str_to_sentence(names(.))) %>%
  printnum() %>%
  apa_table(
  .,
  , caption = "(ref:table-quadratic)"
  , note = "Results are in unit changes on a 1-10 (Censored) scale for social skills for a standard deviation increase in school SES. Full results in supplementary materials. Conduct = conduct problems, peer = peer problems, social = prosocial. Teacher = teacher reported, parent = parent reported."
)

@@

The predictive association of school average SES on social skills was not consistent across the SES gradient (see Table \@ref(table-quadratic)). Significant school average SES by student SES interactions were significant for peer and conduct problems for both teacher and parent reports and for teacher reported prosocial behavior. Interactions are plotted in Figures \@ref(fig:conduct)-\@ref(fig:social). Full model results can be found in supplementary materials. The interaction plots suggest that school context effects were particularly potent for disadvantaged children but school context had minimal impact on social skills for children from advantaged backgrounds. The plots suggest that for the very poorest schools in our sample, a disadvantaged student would have levels of peer problems greater than the threshold for 'close to average' scores and thus potentially of concern [@youth2016scoring]. This same child would be well within the 'close to average' band in a school with an average levels of SES.

@@

Finally, we were not able to identify and compare the relative impact of different mechanisms that may explain the influence of school average socioeconomic status on social skills. As educational psychologists our study is framed in relation to assimilation effects in response to children's peer frames-of-reference. Yet, economic theory tends to emphasize the socialization influence of teachers and educational structures [see \@bowles2001]. Identifying and comparing these mechanisms is an important future direction for research.

>>>>

- name: Philip Parker
  affiliation: '1'
  corresponding: yes
  address: 33 Berry St, North Sydney, NSW, 2060, Australia
  email: philip.parker@acu.edu.au
  role:
  - Conceptualization
  - Formal Analysis
  - Data curation
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Taren Sanders
  affiliation: '1'
  # corresponding: no
  # address: 33 Berry St, North Sydney, NSW, 2060, Australia
  # email: taren.sanders@acu.edu.au
  role:
  - Conceptualization
  - Data curation
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Jake Anders
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Nikki Shure
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: John Jerrim
  affiliation: '2'
  role:
  - Conceptualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Michael Noetel
  affiliation: '1,3'
  role:
  - Visualization
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
- name: Joseph Ciarrochi
  affiliation: '1'
  role:
  - Writing - Original Draft Preparation
  - Writing - Review & Editing
shorttitle: School SES and Social Skills
output:
  pdf: papaja::apa6_pdf
  html_document:
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
  word: papaja::apa6_doc
  html_notebook:
    fig_caption: yes
    toc: yes
    highlight: haddock
    theme: spacelab
authornote: |
  Code for this paper is avaliable from [OSF](https://osf.io/q26ej/?view_only=73f60cea7a9c4e6f8affc412b30df118). Data is avaliable from the [Australian Data Archive](https://dataverse.ada.edu.au/dataverse/ada?q=LSAC).
abstract: |2
  As researchers and policymakers try to understand the consequences of SES for educational and occupational attainment, they increasingly consider social skills to be critical. Yet little research has considered how the school socio-economic context may differentially promote or hinder social skill development. In a representative longitudinal sample of  `r nrow(data)` Australian 8-year olds, we tested the association between school average socioeconomic status and social skills as reported by parents and teachers. All models controlled for prior social skills at age 4, and additional school and student covariates. We found that school context was associated with social skill assimilation: controlling for individual socioeconomic status, children in more advantaged schools had more prosocial behavior and fewer peer and conduct problems. We found a consistent interaction between individual and school average socioeconomic status that suggested assimilation effects were only present for children from low socioeconomic backgrounds. We found that children from low socioeconomic backgrounds enter school with lower average social skills. They are more likely to be enrolled in more disadvantaged schools. Finally, the social skills of children from low socioeconomic backgrounds worsen in low SES contexts. Taking the evidence together, social stratified schools may harm children from low SES backgrounds while not benefiting children from high SES backgrounds.
keywords: social skills; assimilation effects; socioeconomic status; school context
wordcount: 4627
header-includes:
  - \usepackage{hyperref}
bibliography: r-references.bib
urlcolor: blue
floatsintext: no
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Institute for Positive Psychology and Education, Australian Catholic
    University
- id: '2'
  institution: UCL Institute of Education, UCL
- id: '3'
  institution: School of Health and Behavioural Sciences, Australian Catholic University
---

@@

We use data for children, their parents, and their teachers from the B-Cohort and K-Cohort of the Longitudinal Study of Australian Children (LSAC). LSAC is a government-run study of a representative sample of Australian children who were zero-one (B-cohort) or four-five (K-Cohort) years of age in 2004. Both cohorts of children have been followed every two years since [@aifs2015]. LSAC includes linked administration records for student performance in a standardized national numeracy test. We also use government collected data on school average socioeconomic status. Many children in the sample were the only child surveyed (`r school_one`) or were one of two children surveyed (`r school_two`) in their school. By using administrative records, we gain school average socioeconomic status based on the child's $\text{\underline{whole}}$ school grade from a high-quality source, thus avoiding sampling bias present in much school context research. We excluded participants who were not in school (e.g., were home schooled, or were otherwise missing an identifier of which school they attended), were not in Year 3 at the time of testing, or were not eligible to complete national standardized testing (e.g., children with an intellectual disability). Together our total sample was `r nrow(data)` (`r boys` boys) children in Year 3 at school (\~age 8). In the vast majority of cases (98%), parent data came from mothers. A participant flow diagram is presented in [supplementary materials](http://blindedforreview.com/2020_social_skills/supplementary_materials.html) including the number of participants excluded because there were a) not in Year 3 during the age 8 LSAC data collection sweep; b) were not eligible to participate NAPLAN (e.g., due to intellectual disability; or c) were not enrolled in school (e.g., were home schooled).

@@

Social skills were estimated using the peer problems, conduct problems, and prosocial behavior component scores from the SDQ [@goodman1997]. We explored social skills at age 4-5 (for prior social skills; parent report only) and age 8-9 (as primary outcomes) as reported by the child's *parent* and the child's *teacher*. The SDQ asks respondents tfo rate a child's behavior in the last six months on a 3-point scale (not true, somewhat true, and certainly true). Questions ask about the child's peer problems ("Rather solitary, tends to play alone"), conduct problems ("Often fights with other children or bullies them"), and prosociality ("Is kind to younger children"). Greatest lower bound estimates of reliability were all greater than .95 and parallel analysis suggested that a single component was sufficient for each of the parent and teacher and age 4 and age 8 social skills factors. On the basis of this evidence, we used the total scores for these scales as developed by the LSAC administrators. Scores ranged from 0 to 10. These scores were heavily left censored for peer and conduct problems with a preponderance of students being scored as a zero by their parent or teacher. Prosocial behaviors were heavily right censored. Censoring can be viewed as a special type of missing data where scores on $y*$ (the hypothesised true latent distribution of the variable) below or above the bounds are curtailed to fit within the bounds resulting in the observed scores $y$ [@gelman2020regression]. Models accounting for this censoring were used in all cases with results provided on the scale of the latent variable $y*$ believed to underlie the censored variable (hence negative predicted scores or scores over 10 were possible).

@@

There was a relatively small amount of missing data for most variables. However, given the data required responses from both parents and teachers and were linked to administrative records and data collected from both the child's teacher and parent, missing data was inevitable. Missing data was small with the largest missing data proportion for teacher reported social skills at 14%. All other variables had 6% missing data or less (see code book in [supplementary materials](http://blindedforreview.com/2020_social_skills/supplementary_materials.html)). To account for this, we constructed five imputed datasets using a bootstrapped expectation maximization procedure from the Amelia II package [@honaker2011]. These imputations were used in all analyses. All analyses were done using Bayes via the BRMS package in R [@bürkner2017]. The Bayes models were run once for each imputation and then the resulting posterior samples were pooled before estimates and their uncertainty were extracted. Interactions and their associated uncertainties were plotted by taking marginal effect estimates from a random 500 posterior draws for disadvantaged (two standard deviations below the mean of SES), average, and advantaged (two standard deviations above the mean of SES) students [@gelman2020regression].

@@

Here $X$ is a matrix of individual level predictors for student $i$ including individual SES, prior social skills, gender, cohort, geographic location, and an NAPLAN achievement index. Prior social skills is particularly critical as this provide stronger conclusions that school context rather than selection effects account for the influence of school average SES on student social skills. Put simply the estimate of school average SES can be interpreted as the influence of school context on the change in childrens' social skills from age 4 to age 8. $U$ is a matrix of school level predictors for school $j$ including school section and the aforementioned critical variable *school SES*. Note that we predict $y^{*}_{i}$ which is the latent continuous variable underlying the observed variables which are defined as:

@@

In order to provide a context for the main analyses we first aimed to show: a) that children from advantaged backgrounds enter school with better social skills (as measured by their parents) and b) that children in Australia tend to be schooled in socially stratified schools. Student SES is slightly correlated with prior prosocial behaviour (`r glue::glue("{format(des_social$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_social$prior_ses$fixed[3], digits = 2)}, {format(des_social$prior_ses$fixed[4], digits = 2)}]")`) but more strongly and negatively correlated with prior conduct (`r glue::glue("{format(des_conduct$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_conduct$prior_ses$fixed[3], digits = 2)}, {format(des_conduct$prior_ses$fixed[4], digits = 2)}]")`) and peer (`r glue::glue("{format(des_peer$prior_ses$fixed[1], digits = 2)} 95% CI[{format(des_peer$prior_ses$fixed[3], digits = 2)}, {format(des_peer$prior_ses$fixed[4], digits = 2)}]")`) problems. Children from lower SES backgrounds also tended to enter schools with children from similar backgrounds (`r glue::glue("{format(des_social$sch_ses$fixed[1], digits = 2)} 95% CI[{format(des_social$sch_ses$fixed[3], digits = 2)}, {format(des_social$sch_ses$fixed[4], digits = 2)}]")`). Put simply, disadvantaged children tended to enter school with lower social skills and the school they entered tended poorer on average.

@@

linear_table %>%
  set_names(str_to_sentence(names(.))) %>%
  printnum() %>%
  apa_table(
  .,
  , caption = "(ref:table-linear)"
  , note = "Results are in unit changes on a 1-10 (Censored) scale for social skills for a standard deviation increase in school SES. Full results in supplementary materials. Conduct = conduct problems, peer = peer problems, social = prosocial. Teacher = teacher reported, parent = parent reported.",
  booktabs = TRUE
)

@@

We next predicted social skills with school average SES controlling for individual SES, a range of demographic covariates and academic performance measures, and social skills at age 4. Results for school average SES are presented under in Table \@ref(tab:table-1) (the full model results are in [supplementary materials](http://blindedforreview.com/2020_social_skills/supplementary_materials.html)). Because we control for prior social skills, the effects of school average SES in these models can be interpreted as predicting change or development in social skills from age 4 (at or just prior to school enrollment) to age 8 (Year 3). School average SES negatively predicted conduct problems and positively predicted prosocial behavior for both parent and teacher reported social skills. School average SES also negatively predicted peer problems. Results from either teacher or parent provided fairly consistent evidence of the influence of school SES context on social skills (or more specifically change in social skills from age 4 to age 8). Interestingly, the association of school average SES with social skills was similar in strength to the association of individual SES with social skills (see supplementary materials for full results). The effect sizes were equivalent to approximately a $10^{th}$ of the median absolute deviation in social skills.

@@

interaction_table %>%
  set_names(str_to_sentence(names(.))) %>%
  printnum() %>%
  apa_table(
  .,
  , caption = "(ref:table-quadratic)"
  , note = "Results are in unit changes on a 1-10 (Censored) scale for social skills for a standard deviation increase in school SES. Full results in supplementary materials. Conduct = conduct problems, peer = peer problems, social = prosocial. Teacher = teacher reported, parent = parent reported.",
  booktabs = TRUE
)

@@

The predictive association of school average SES on social skills was not consistent across the SES gradient (see Table \@ref(tab:table-2)). Significant school average SES by student SES interactions were significant for peer and conduct problems for both teacher and parent reports and for teacher reported prosocial behavior. Interactions are plotted in Figures \@ref(fig:peer)-\@ref(fig:social). Full model results can be found in supplementary materials. The interaction plots suggest that school context effects were particularly potent for disadvantaged children but school context had minimal impact on social skills for children from advantaged backgrounds. The plots suggest that for the very poorest schools in our sample, a disadvantaged student would have levels of peer problems greater than the threshold for 'close to average' scores and thus potentially of concern [@youth2016scoring]. This same child would be well within the 'close to average' band in a school with an average levels of SES.

@@

Finally, we were not able to identify and compare the relative impact of different mechanisms that may explain the influence of school average socioeconomic status on social skills. As educational psychologists our study is framed in relation to assimilation effects in response to children's peer frames-of-reference. Yet, economic theory tends to emphasize the socialization influence of teachers and educational structures [@bowles2001]. Identifying and comparing these mechanisms is an important future direction for research.

### 2020-11-06 supplementary_materials.Rmd
clean full draft
Ed Researcher Version

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(targets)
library(scales)
library(tidyverse)
library(DT)

```

@@

```{r}
tar_load(supp_linear)
supp_linear %>% 
  datatable(filter = 'top', caption = "Table S1. Full Linear Model Outputs")
```

@@

```{r}
tar_load(supp_interaction)
supp_interaction %>%
  datatable(filter = 'top', caption = "Table S2. Full Interaction Model Outputs")
```

@@

```{r, child="data/social_skills_codebook.Rmd"}

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(targets)
library(scales)
library(tidyverse)
library(DT)
library(knitr)
```

# Participant Flow Diagram

```{r}
library(magick)
pdf = magick::image_read(here::here("fig","flow.pdf"))
image_convert(pdf, "png")
```

@@

```{r}
tar_load(supp_linear)
supp_linear %>% 
  datatable(filter = 'top', caption = "Table S1. Full Linear Model Outputs") %>%
    formatRound(columns=4:6, digits=3)
```

@@

```{r}
tar_load(supp_interaction)
supp_interaction %>%
  datatable(filter = 'top', caption = "Table S2. Full Interaction Model Outputs") %>%
    formatRound(columns=4:6, digits=3)
```

@@

```{r, child="data/social_skills_codebook.Rmd"}
```
